\subsection{Journal Service}

\datedsubsectionnarrow{2021 -- present}
{Journal of Open Source Software}
{\textbf{Editor}}
{}

\datedsubsectionnarrow{2020 -- present}
{}
                     {\textbf{Reviewer}}{Phys. Rev. Lett. (1), Comp. Phys. Comm. (1), PRX Energy (1), APL Mach. Learn. (1), J. Phys. Chem. (1), Chem. Mater. (1), J.Phys. Chem. Lett. (1), Phys. Rev.  Mater. (6), Comput. Mater. Sci. (1), IEEE J-PV (1), Nat. Comp. Sci. (1), Npj Comput. Mater. (1)}

\vspace{-1mm}
\subsection{Conference Service: Organization}
%\vspace{-1mm}
\datedsubsectionnarrow{2024 -- present}
                      {JuliaCon Global}
                      {\textbf{Co-chair}, Local Committee}
                        {}

\datedsubsectionnarrow{2024 -- present}
{Electronic Materials Conference}
{\textbf{Invited Organizer}}
{}

\datedsubsectionnarrow{2024}
{MolSSI workshop on Julia for Computational Molecular and Materials Science}
{\textbf{Lead Organizer}}
{}

\datedsubsectionnarrow{2019 -- 2020}
{Pittsburgh Conference for Undergraduate Women in Physics}
{\textbf{Organizer}}
{}

\datedsubsectionnarrow{2015}
{Solar Energy Technology \& Innovation in Mexico Workshop}
{\textbf{Organizer}}
{}

\datedsubsectionnarrow{2011 -- 2012}
{Northeast Conference for Undergraduate Women in Physics}
{\textbf{Treasurer, Organizer}}
{}

\vspace{-1mm}
\subsection{Conference Service: Other}

\datedsubsectionnarrow{May 2023}
{CMU Meeting of the Minds}
{\textbf{Poster Session Judge}}
{}


\datedsubsectionnarrow{May 2023}
{CMU MSE Graduate Symposium}
{\textbf{Technical Presentation Judge}}
{}

\datedsubsectionnarrow{2023 -- 2024}
{CMU Energy Week}
{\textbf{Poster Session Judge}}
{}


\datedsubsectionnarrow{March 2022}
{Scientific Machine Learning Webinar Series}
{\textbf{Session Chair}}
{}

\datedsubsectionnarrow{March 2022}
{APS March Meeting}
{\textbf{Session Chair}, B67: Advanced Approaches in Modeling and Simulation of Defects}
{}

\datedsubsectionnarrow{July 2021}
{JuliaCon}
{\textbf{Session Chair, Volunteer}}
{}

\datedsubsectionnarrow{2021 -- present}
{JuliaCon}
{\textbf{Reviewer}}
{}

\datedsubsectionnarrow{2019}
{NeurIPS ML4PS Workshop}
{\textbf{Reviewer}}
{}

\datedsubsectionnarrow{October 2019}
{Pitt Science2019}
{\textbf{Poster Session Judge}}
{}

\datedsubsectionnarrow{January 2015}
{Northeast Conference for Undergraduate Women in Physics}
{\textbf{Panelist}}
{}



\vspace{-2mm}
\subsection{Leadership and University Service}
%\vspace{-1mm}
\datedsubsectionnarrow{2023 -- present}
                      {CMU MSE Department}
                      {\textbf{Member}, Undergraduate Education Committee}
                      {}

\datedsubsectionnarrow{2023 -- present}
                      {CMU Libraries}
                      {\textbf{Member}, Open Science Advisory Board}
                      {}

\datedsubsectionnarrow{2023 -- present}
                      {CMU Spring Carnival}
                      {\textbf{Design Judge}, Buggy Design Competition}
                      {}
                      
\datedsubsectionnarrow{October 2023}
                      {CMU MSE Rising Stars Workshop}
                      {\textbf{Panelist, Mentor}}
                      {}


\datedsubsectionnarrow{2022 -- 2024}
{American Geophysical Union}
{\textbf{Working Group Chair}, Notebooks Now! Initiative}
{}

\datedsubsectionnarrow{2018 -- 2019}
{MIT School of Engineering}
{\textbf{Member}, Graduate Student Advisory Group for Engineering}
{}
%\vspace{-0.3mm}
\datedsubsectionnarrow{2018 -- 2019}
{MIT DMSE}
{\textbf{Co-President}, Womxn of Materials Science}
{}
%\vspace{-0.3mm}
\datedsubsectionnarrow{2017}
{MIT Energy Initiative}
{\textbf{Mentor}, Solar Spring Break (service trip)}
{}

\datedsubsectionnarrow{2016 -- 2019}
{MIT Energy Initiative}
{\textbf{Member}, Energy Education Task Force}
{}

\datedsubsectionnarrow{2016 -- 2019}
{MIT Office of Sustainability}
{\textbf{Member}, Solar Test Bed Steering Committee}
{}

\datedsubsectionnarrow{2015 -- 2017}
{MIT Energy Club}
{\textbf{Co-Leader}, Solar/Grid Community}
{}

\datedsubsectionnarrow{2012 -- 2013}
{Yale Office of Sustainability}
{\textbf{Co-Leader}, Project Bright}
{}

\datedsubsectionnarrow{2012}
{Yale Physics Department}
{\textbf{Co-President}, Society of Physics Students}
{}

\vspace{-2mm}
\subsection{Outreach and Other Service}
%\vspace{-1mm}
\datedsubsectionnarrow{2022 -- present}
{Prison Mathematics Project}
{\textbf{Mentor}}
{}

\datedsubsectionnarrow{May 2022}
{Julia Gender Inclusive}
{\textbf{Guest Speaker}}
{}

\datedsubsectionnarrow{2021 -- present}
{Skype a Scientist}
{\textbf{Volunteer}}
{}

\datedsubsectionnarrow{2021 -- 2022}
{Regeneron ISEF}
{\textbf{Grand Award Judge}, Materials Science Division}
{}

\datedsubsectionnarrow{Sumer 2021}
{Google Summer of Code}
{\textbf{GSoC Mentor}, Julia Language (Chemellia)}
{}

\datedsubsectionnarrow{March 2014}
{Cambridge Hands-On Science (CHaOS)}
{\textbf{Demonstrator}}
{}
